\chapter*{Useful Texts \& Further Readings}

\section*{Books}
\begin{itemize}
    \item J. Wess and J. Bagger, \textit{Supersymmetry \& Supergravity}, Princeton, USA: Univ. Pr. (1992) 259 p. 
    \item P. C. West, \textit{Introduction To Supersymmetry \& Supergravity}, Singapore: World Scientific (1990) 425 p.
    \item S. Weinberg, \textit{The Quantum Theory Of Fields. Vol. 3: Supersymmetry}, Cambridge, UK: Univ. Pr. (2000) 419 p.
    \item J. Terning \textit{Modern Supersymmetry: Dynamics \& Duality}, Oxford, UK: Clarendon (2006) 324 p.
\end{itemize}

\section*{Reviews \& Lecture Notes}
\begin{itemize}
    \item A. Bilal, \href{https://arxiv.org/pdf/hep-th/0101055.pdf}{Introduction to supersymmetry}.
    \item M. F. Sohnius, \href{https://www.sciencedirect.com/science/article/abs/pii/0370157385900237?via\%3Dihub}{Introducing Supersymmetry}.
    \item S. P. Martin, \href{https://arxiv.org/pdf/hep-ph/9709356.pdf}{A Supersymmetry Primer}.
    \item J. Figueroa-O’Farrill, \href{https://arxiv.org/pdf/hep-th/0109172.pdf}{BUSSTEPP Lectures on Supersymmetry}.
    \item P. Argyres, \href{https://homepages.uc.edu/~argyrepc/cu661-gr-SUSY/index.html}{An Introduction to Global Supersymmetry}.
    \item M. J. Strassler, \href{https://arxiv.org/pdf/hep-th/0309149.pdf}{An Unorthodox Introduction to Supersymmetric Gauge Theory}.
    \item K. A. Intriligator and N. Seiberg, \href{https://arxiv.org/pdf/hep-th/9509066.pdf}{Lectures On Supersymmetric Gauge Theories \& Electric-Magnetic Duality}, Nucl. Phys. Proc. Suppl. 45BC (1996) 28.
    \item M. Bertolini, \href{https://people.sissa.it/~bertmat/susycourse.pdf}{Lectures on Supersymmetry}.
    \item R. Argurio, \href{http://homepages.ulb.ac.be/~rargurio/susycourse.pdf}{Introduction to Supersymmetry}.
\end{itemize}